Data preparation

### 2024-03-19 paper1_jiturra.Rmd
ajustes pdf

_Data_

_Variables_

_Method_

@@

```{r, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class'}
int_homo <- digclas1_VW_7
df_pred1 <- 
  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.1),
                                 dclass3res_V = levels(dfreg$dclass3res_V)))
# names(df_pred1)
df_pred1 %>% 
ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_y_continuous(limits = c(50,80))+
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
       x="Network homogeneity",y="Redistributive preferences") +
  theme(legend.position = "none", legend.title = element_blank())

@@

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
  egal = egal2,
  # starts_with("class3"),
  # starts_with("digclass3"),
  # starts_with("dclass3"),
  # starts_with("homclass"),
  dclass3res_V,
  dclass3spo_V,
  homclass3_V_res,
  know_total,
  socialtrust,
  Q03pcm,
  edyears,
  female,
  agenum,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         gini_disp=gini_disp*100) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN")

@@

dfreg$dclass3spo_V <- car::recode(dfreg$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
homo_V_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_controls <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +loggdppercapita + rel_red + gv_spen +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_full <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +loggdppercapita + rel_red + gv_spen +
         homclass3_V_gc*
         dclass3res_V*
         gini_disp +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

digclas1_macro <- list(homo_V_gini,homo_V_gini_controls,homo_V_gini_full)

ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP (per capita)",
              rel_red = "Relative Redistribution",
              gv_spen = "Government spending (percentage of GDP)",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity x Working Class",
              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity x Intermediate Class x Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity x Working Class x Income Inequality")

texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive preferences",
       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
       caption.above = T,leading.zero = T,single.row = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 2:3, "Homogeneity x Social Class"=8:9, "Homogeneity x Social Class x Income Inequality"=11:12),
       float.pos = "h!",
       use.packages = F)
```

@@

>>>>

## Data {-}

## Variables {-}

### _Individual level_ {-}

* **Social class** (Erikson & Goldthorpe, 1992): EGP Class Scheme, based on ISCO-08 codes for (i) occupations and using the algorithm that considers (ii) self-employment status and (iii) number of workers (Ganzeboom & Treiman, 2003). As a result, three big classes are created: Service Class (I+II),  Intermediate Class (III+IV), and Working Class (VI+VII).

* **Class-based network segregation** [@otero_open_2021]: Based on the ten occupations of the position generator, three status groups are created to mirror the three social classes described above:
  - High: Lawyer, Executive of a large firm, and Human resource manager
  - Middle: School teacher, Police officer and Nurse
  - Low: Car mechanic, Bus driver, Hairdresser, and Home or office cleaner

After this, we calculated the number of social ties for each status group. Consequently, the group closer to their class position obtains a proxy of the number of ingroup social ties. Finally, the number of ingroup ties is divided by the total number of contacts to provide a measure of network homogeneity that seeks to represent the share of similar social ties within the personal network. Here, zero represents that all social ties are *different* (heterogeneity), while one means that all social contacts are similar (homogeneity). In substantial terms, higher values represent greater social distance from other social classes in society.

### _Macro level_ {-}

* Income Inequality (post-taxes): Gini Index from the World Income Inequality Dataset (https://wid.world/)

* Gross Domestic Product per capita (WID, 2022)

* Size of the welfare state [see @edlund_democratic_2015]
  - Current Redistribution (Solt, 2020)
  - Tax revenue, as percentage of GDP (ILO)
  - Welfare expenditure, as Percentage of GDP (ILO)

## Method {-}

Multilevel regression models with random and fixed effects. For the cross-level interactions we include random slopes and all variables are group-mean centered (CWC)

@@

```{r, fig.dim=c(10,5),fig.cap='Linear Predictions for Network Homogeneity on Redistributive Preferences by Social Class'}
int_homo <- digclas1_VW_7
df_pred1 <- 
  predictions(int_homo, condition = c("homclass3_V_res","dclass3res_V"),
              newdata = datagrid(homclass3_V_res = seq(min(dfreg$homclass3_V_res), max(dfreg$homclass3_V_res), by= 0.1),
                                 dclass3res_V = levels(dfreg$dclass3res_V)))
# names(df_pred1)
df_pred1 %>% 
ggplot(aes(y =estimate,x=homclass3_V_res, fill=dclass3res_V, color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=1,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=2,color="black") +
  facet_grid(~factor(dclass3res_V, levels=
                       c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"),
                     c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))) +
  scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
  scale_y_continuous(limits = c(50,80))+
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo)),
       x="Class-based network homogeneity",y="Redistributive preferences") +
  theme(legend.position = "none", legend.title = element_blank())

@@

load(here::here("input/data/proc/study1_country.RData"));df1 <- df2

df1$dclass3spo_V <- car::recode(df1$dclass3spo_V,"NA='No information (Missing, No partner)'",levels = c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)","No information (Missing, No partner)"))

dfreg <- df1 %>% dplyr::select(
  egal = egal2,
  # starts_with("class3"),
  # starts_with("digclass3"),
  # starts_with("dclass3"),
  # starts_with("homclass"),
  dclass3res_V,
  dclass3spo_V,
  homclass3_V_res,
  know_total,
  socialtrust,
  Q03pcm,
  edyears,
  female,
  agenum,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  "gini_mkt",
  gv_spen,
  rel_red,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  rgdpna,
  gdppercapita,
  oecd,
  country2, country, country3,
) %>%
  mutate(logrgdpna = log(rgdpna),
         loggdppercapita=log(gdppercapita),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         gini_disp=gini_disp*100) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") %>% 
  na.omit()

# dfreg %>% dplyr::select(gini_disp,rel_red,abs_red,ilo_taxrev,ilo_govspe) %>% tab_corr()

dfreg$wstate1 <- scale(scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
dfreg$wstate2 <- scale(scale(dfreg$abs_red) + scale(dfreg$ilo_taxrev) + scale(dfreg$ilo_govspe))
# dfreg$wstate <- scale(dfreg$gv_spen)

@@

# dfreg$gini_disp <- scale(dfreg$gini_disp)

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------
homo_V_gini <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +loggdppercapita +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_wstate2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +loggdppercapita + wstate2+
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_gdp_controls <-
  lmer(egal~
         homclass3_V_gc+
         know_total_gc+
         socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +loggdppercapita + wstate2 +
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

homo_V_gini_full2 <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         socialtrust_gc+
         dclass3res_V+dclass3spo_V+
         female_gc+agenum_gc+age2_gc+
         edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
         union_gc+workst_gc+
         gini_disp +loggdppercapita + wstate2+
         homclass3_V_gc*
         dclass3res_V*
         gini_disp + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

digclas1_macro <- list(homo_V_gini,
                       homo_V_gini_gdp,
                       homo_V_gini_gdp_wstate2,
                       homo_V_gini_full2)

ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP (per capita)",
              # ilo_taxrev = "Tax revenue (percentage of GDP)",
              # ilo_govspe = "Government spending (percentage of GDP)",
              # abs_red = "Redistribution",
              # wstate1="Size of Welfare State (tax+spend)",
              wstate2="Size of the welfare state",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity x Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity x Working Class",
              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity x Intermediate Class x Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity x Working Class x Income Inequality")

texreg(digclas1_macro,stars = c(0.001, 0.01, 0.05, 0.1),symbol = "+",scalebox = 0.60,
       caption = "Multilevel models for Income Inequality, Network segregation and Redistributive preferences",
       custom.note = "%stars. Models include sampling weights and individual level controls centered within cluster (group mean)",
       caption.above = T,leading.zero = T,single.row = T,
       custom.coef.map = ccoef,
      groups = list("Social Class (Ref.= Service Class)" = 2:3,"Macro-level factors"=4:6, "Homogeneity x Social Class"=7:8, "Homogeneity x Social Class x Income Inequality"=10:11),
       float.pos = "h!",
       use.packages = F)
```

```{r, fig.dim=c(12,6),fig.cap='Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality'}
### Predicted values homo*class*GiniD ---------------------------------------
# ginid_max<- round(max(dfreg$gini_disp) ,2)
# ginid_min<- round(min(dfreg$gini_disp),2)

ginid_max<- round(mean(dfreg$gini_disp) + sd(dfreg$gini_disp)  ,2)
ginid_min<- round(mean(dfreg$gini_disp) -sd(dfreg$gini_disp) ,2)
ginid_mea<- round(mean(dfreg$gini_disp),2)

df_pred_giniD_gc <-
  predictions(
    homo_V_gini_full2,newdata = datagrid(
      gini_disp = c(ginid_min, ginid_mea, ginid_max),
      wstate2=mean(dfreg$wstate2),
      homclass3_V_gc = seq(min(dfreg$homclass3_V_gc), max(dfreg$homclass3_V_gc), by= 0.1),
      dclass3res_V=levels(dfreg$dclass3res_V)
    )
  )

df_pred_giniD_gc <- as.data.frame(df_pred_giniD_gc)
df_pred_giniD_gc$gini_disp <- factor(df_pred_giniD_gc$gini_disp,labels = c("Gini (-1SD)","Gini (Mean)", "Gini (+1SD)"))

df_pred_giniD_gc <- df_pred_giniD_gc %>% filter(dclass3res_V!="Intermediate class (III+IV)")

df_pred_giniD_gc %>% 
  ggplot(aes(y=estimate,x=homclass3_V_gc, fill=dclass3res_V,color=dclass3res_V,ymin=conf.low, ymax=conf.high)) +
  geom_ribbon(alpha=0.8,size=0.7,linetype="solid",color="black") +
  geom_line(size=1,color="black") +
  geom_point(size=3, shape = 21,color="black") +
  facet_wrap(~gini_disp) +
  labs(y = "Preferences for Redistribution",
       x="Class-based network homogeneity (CWC)",
       # title = "Three-way interaccion effects for Preferences for Redistribution, Network segregation, Social class and Income Inequality"
       ) +
  # scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Income inequality (post-tax)", breaks = NULL, labels = NULL)) +
 # scale_fill_manual(values=c("#323232","#989898","#CCCCCC"))+
  # scale_color_manual(values=c("#323232","#989898","#CCCCCC"))+
   scale_fill_manual(values=c("#323232","#CCCCCC"))+
  scale_color_manual(values=c("#323232","#CCCCCC"))+
  theme(legend.position="bottom",
        legend.direction = "horizontal",
        axis.text=element_text(size=15),
        legend.title = element_blank(),
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"))
```

@@

```{r oldcode, eval=FALSE, include=FALSE}

# homo_V_gini_gdp_tax <- 
#   lmer(egal~ 
#          homclass3_V_gc+
#          know_total_gc+
#          socialtrust_gc+
#          dclass3res_V+dclass3spo_V+
#          female_gc+agenum_gc+age2_gc+
#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
#          union_gc+workst_gc+
#          gini_disp +loggdppercapita + ilo_taxrev +
#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
# 
# 
# homo_V_gini_gdp_govsp <- 
#   lmer(egal~ 
#          homclass3_V_gc+
#          know_total_gc+
#          socialtrust_gc+
#          dclass3res_V+dclass3spo_V+
#          female_gc+agenum_gc+age2_gc+
#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
#          union_gc+workst_gc+
#          gini_disp +loggdppercapita + ilo_govspe +
#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
# 
# 
# homo_V_gini_gdp_redis <- 
#   lmer(egal~ 
#          homclass3_V_gc+
#          know_total_gc+
#          socialtrust_gc+
#          dclass3res_V+dclass3spo_V+
#          female_gc+agenum_gc+age2_gc+
#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
#          union_gc+workst_gc+
#          gini_disp +loggdppercapita + abs_red +
#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
# 
# homo_V_gini_gdp_controls <-
#   lmer(egal~
#          homclass3_V_gc+
#          know_total_gc+
#          socialtrust_gc+
#          dclass3res_V+dclass3spo_V+
#          female_gc+agenum_gc+age2_gc+
#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
#          union_gc+workst_gc+
#          gini_disp +loggdppercapita + ilo_taxrev + ilo_govspe + abs_red +
#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
# 
# 
# homo_V_gini_gdp_wstate1 <- 
#   lmer(egal~ 
#          homclass3_V_gc+
#          know_total_gc+
#          socialtrust_gc+
#          dclass3res_V+dclass3spo_V+
#          female_gc+agenum_gc+age2_gc+
#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
#          union_gc+workst_gc+
#          gini_disp +loggdppercapita + wstate1+
#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

# homo_V_gini_full <- 
#   lmer(egal~ 
#          homclass3_V_gc+
#          know_total_gc+
#          socialtrust_gc+
#          dclass3res_V+dclass3spo_V+
#          female_gc+agenum_gc+age2_gc+
#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
#          union_gc+workst_gc+
#          gini_disp +loggdppercapita + ilo_taxrev + ilo_govspe + abs_red +
#          homclass3_V_gc*
#          dclass3res_V*
#          gini_disp + 
#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
# 
# homo_V_gini_full1 <- 
#   lmer(egal~ 
#          homclass3_V_gc+
#          know_total_gc+
#          socialtrust_gc+
#          dclass3res_V+dclass3spo_V+
#          female_gc+agenum_gc+age2_gc+
#          edyears_gc+Q03pcm_2_gc+Q03pcm_3_gc+Q03pcm_NA_gc+
#          union_gc+workst_gc+
#          gini_disp +loggdppercapita + wstate1+
#          homclass3_V_gc*
#          dclass3res_V*
#          gini_disp + 
#          (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)
```

### 2024-03-19 procesamiento/02-prod_prep-macro.Rmd
ajustes pdf

# Convert from wide to long format
long_ilo_tax <- ilo_tax %>%
  select(ccode,Y_2010:Y_2016) %>% 
  pivot_longer(cols = starts_with("Y_"),
               names_to = "year",
               names_prefix = "Y_",
               values_to = "ilo_taxrev")
# long_ilo_tax$country <- countrycode::countrycode(sourcevar = long_ilo_tax$ccode,origin = "iso3n",destination = "iso3c")

@@

>>>>

# Convert from wide to long format
long_ilo_tax <- ilo_tax %>%
  select(ccode,Y_2010:Y_2016) %>% 
  pivot_longer(cols = starts_with("Y_"),
               names_to = "year",
               names_prefix = "Y_",
               values_to = "ilo_taxrev")
long_ilo_tax$ilo_taxrev <- as.numeric(long_ilo_tax$ilo_taxrev)

@@

long_ilo_spe$ilo_govspe <- as.numeric(long_ilo_spe$ilo_govspe)
